Worflow

### 2017-06-06 R/workflow.Rmd
add a bit of writing

FP: yes, I agree.

@@

- Dimensionality reduction using zinbwave to get W which should capture the biology,
- Cluster cells using clusterExperiment on W to get the cluster labels,   
- Get lineage using slingshot on W and cluster labels from clusterExperiment,  
- Get DE genes between lineages/clusters.

@@

To cluster and get lineages we want to reduce the dimension of the data. We are going to use zinbwave to do so. First, let's fit zinbwave with first K = 0 to compute normalized values (i.e. deviance residuals) adjusted for batches. We could also adjust for gene length or GC content here. We then fit zinbwave to get the dimensionality reduced matrix W specifying the number of dimension K = 50. Eventually, we will call zinbwave just once where we would have an argument in zinbFit like "compute_normalized_values" in c(TRUE, FALSE). For K = 0 and K = 50, we correct for batch effect including batches in X.

@@

We use deviance residuals as normalized values for visualization. FP: explain rational: K=0 so residuals capture the bio adjusting for batch. Let's check that deviance residuals look ok.

>>>>

FP: yes, I agree. We would ideally work with a SummarizedExperiment object where we would add an assay for the normalized values.

@@

- Dimensionality reduction using zinbwave to get W which should capture the biology, 
- Cluster cells using clusterExperiment on W to get the cluster labels,
- Get lineage using slingshot on W from zinbwave and cluster labels from clusterExperiment,  
- Get DE genes between lineages/clusters using a tool like MAST or edgeR.

@@

To cluster and get lineages we want to reduce the dimension of the data. We are going to use zinbwave to do so. First, let's fit zinbwave first with K = 0 to compute normalized values (i.e. deviance residuals) adjusted for batches. We could also adjust for gene length or GC content here. We then fit zinbwave to get the dimensionality reduced matrix W specifying the number of dimension K = 50. We could try different K here (maybe K = 100). We could also try to see if adding commondispersion = FALSE change the results.Eventually, we will call zinbwave just once where we would have an argument in zinbFit like "compute_normalized_values" in c(TRUE, FALSE).

For K = 0 and K = 50, we correct for batch effect including batches in X.

@@

We use deviance residuals as normalized values for visualization. We use K = 0 so residuals capture the biology while adjusting for gene and cell level covariates, here we have only cell-level covariates (batches). Let's check that deviance residuals look ok.
